Tropical Andes plant species BIEN Ranges

### 2023-07-25 archive/MappingGBIF_Richness.RMD
move old code to archive

# Read in Data
```{r}
NorthAndes_GBIF_plant_occ <- read.csv(file.path(data_path,"TropAndes_GBIF_plant_occ.csv"))
NorthAndes_GBIF_frugivore_occ <- read.csv(file.path(data_path,"TropAndes_GBIF_frugivore_occ.csv"))
```

@@

```{r}
plants.sf <- st_as_sf(NorthAndes_GBIF_plant_occ, coords = c("decimalLongitude", "decimalLatitude"), crs = 4326)
```

```{r}
frugivores.sf <- st_as_sf(NorthAndes_GBIF_frugivore_occ, coords = c("decimalLongitude", "decimalLatitude"), crs = 4326)
```

>>>>

# Read in Data
```{r}
TropicalAndes_GBIF_plant_occ <- read.csv(file.path(data_path,"TropAndes_GBIF_plant_occ.csv"))
TropicalAndes_GBIF_frugivore_occ <- read.csv(file.path(data_path,"TropAndes_GBIF_frugivore_occ.csv"))
```

@@

```{r}
plants.sf <- st_as_sf(TropicalAndes_GBIF_plant_occ, coords = c("decimalLongitude", "decimalLatitude"), crs = 4326)
```

```{r}
frugivores.sf <- st_as_sf(TropicalAndes_GBIF_frugivore_occ, coords = c("decimalLongitude", "decimalLatitude"), crs = 4326)
```
